Capstone Movielens Report

### 2025-12-08 reports/capstone-movielens.site/05.appendix.Rmd
UMGYDE Model description started (prototype added to Appendix A).

In *This Project*, this function is used internally in the [model.tune.param_range](#func.model.tune.param_range) function described in *This Section* below.
:::

@@

This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default) of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.

@@

::: {.noteblock data-latex=""}
In the code snippet above, the function `calc_date_general_effect` is called internally from the [train_UMGY_effect](#func.train_UMGY_effect) function described below.
:::
:::

@@

This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) of the user ratings using the _5-Fold Cross Validation_ and is intended to be used in other functions and scripts (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.

@@

Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in *This Section*).

@@

::: {.noteblock data-latex=""}
In the above code snippet, the `train_UMGY_effect.cv` function is called internally from the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function, along with the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (both described below in [UMGYE Model: Regularization] section and *This Section*, respectively).
:::
:::

@@

Under the hood, this function internally calls the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in *This Section*).

@@

::: {.noteblock data-latex=""}
This helper function is used internally in the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function (described below in *This Section*) as shown in the [Usage](#func.calc_UMGY_effect_MSE.usage) subsection of *This Function's Description Section* below.
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above, the function `calc_UMGY_effect_MSE` is called internally from the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function described below in *This Section*.
:::
:::

@@

::: {.noteblock data-latex=""}
This helper function is used internally in the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (described below in *This Section*) as shown in the [Usage](#func.calc_UMGY_effect_MSE.cv.usage) subsection of *This Function's Description Section* below.
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above, the function `calc_UMGY_effect_MSE.cv` is called internally from the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described below in *This Section*.
:::
:::

@@

>>>>

In *This Project*, this function is used internally in the [model.tune.param_range](#func.model.tune.param_range) function described below in this section.
:::

@@

This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default) of the user ratings using a *training dataset* passed in the [train_set](#func.calc_date_general_effect.args.train_set) argument, and is intended for use in other helper functions (such as [train_UMGY_effect](#func.train_UMGY_effect)), described below in this section.

@@

::: {.noteblock data-latex=""}
In the code snippet above, the function `calc_date_general_effect` is called internally from the [train_UMGY_effect](#func.train_UMGY_effect) function described below in this section.
:::
:::

@@

This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) of the user ratings using the _K-Fold Cross Validation_ and is intended to be used in other custom functions (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.

@@

Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).

@@

::: {.noteblock data-latex=""}
In the above code snippet, the `train_UMGY_effect.cv` function is called internally from the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function, along with the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (both described below in [UMGYE Model: Regularization] section and this section, respectively).
:::
:::

@@

Under the hood, this function internally calls the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).

@@

::: {.noteblock data-latex=""}
This helper function is used internally in the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_effect_MSE.usage) subsection of *This Function's Description Section* below.
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above, the function `calc_UMGY_effect_MSE` is called internally from the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function described below in this section.
:::
:::

@@

::: {.noteblock data-latex=""}
This helper function is used internally in the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_effect_MSE.cv.usage) subsection of *This Function's Description Section* below.
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above, the function `calc_UMGY_effect_MSE.cv` is called internally from the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described below in this section.
:::
:::

@@

### UMGYDE Model: Utility Functions
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) script on _GitHub_.
:::

#### [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L4) Function {#func.calc_day_general_effect}
\

This is a helper function that computes the *Day General Effect(hereafter DG Effect or DGI for short)* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) of user ratings on a *given day since the earliest record* in the `edx` dataset, using a *training dataset* passed in the [train_set](#) argument, and is intended for use in other helper functions such as [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) (both described below in this section).

::: { #func.calc_day_general_effect.usage .sidebar }
##### Usage
\
```{r eval=FALSE}
  train_set |> 
    calc_day_general_effect(lambda) |>
    calc_UMGY_SmoothedDay_effect(degree, span)
```

::: {.noteblock data-latex=""}
In the code snippet above, the function `calc_day_general_effect` is called internally along with the [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function from the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function (both described below).
:::
:::

::: { #func.calc_day_general_effect.args .sidebar }
##### Arguments
\

::: { #func.calc_day_general_effect.args.train_set .sidebar }
  - **train_set:** Training dataset;

:::
::: { #func.calc_day_general_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

::: { #func.calc_day_general_effect.details .sidebar }
##### Details
\

The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_day_general_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::

::: { #func.calc_day_general_effect.value .sidebar }
##### Value
\

Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) *Date General Effect*.
:::

::: { #func.calc_day_general_effect.code .sidebar }
##### Source Code
\

Below is a slightly simplified version of the source code of the [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L4) function:
```{r eval=FALSE}
calc_day_general_effect <- function(train_set, lambda = 0){
  gday_effect <- train_set |> 
    left_join(edx.user_effect, by = "userId") |>
    left_join(rglr.UM_effect, by = "movieId") |>
    left_join(rglr.UMG_effect, by = "movieId") |>
    left_join(date_days_map, by = "timestamp") |>
    left_join(rglr.UMGY_effect, by='year') |>
    mutate(resid = rating - (mu + a + b + g + ye)) |>
    group_by(days) |>
    summarise(de = mean_reg(resid, lambda), 
              year = mean(year))

  if(lambda == 0) put_log("Function `calc_day_general_effect`:
Day General Effect has been computed.")
  else put_log1("Function `calc_day_general_effect`:
Day General Effect has been computed for lambda: %1...",
                lambda)
  gday_effect
}
```

::: {.noteblock data-latex=""}
The complete source code of the [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L4) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L4) script on _GitHub_.
:::
:::

#### [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L33) Function {#func.calc_day_general_effect.cv}
\

This is a helper function that calculates the *Day General Effect* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) of the user ratings using the _5-Fold Cross Validation_ and is intended to be used in other custom functions (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.

::: { #func.calc_day_general_effect.cv.usage .sidebar }
##### Usage
\
```{r eval=FALSE}
calc_day_general_effect.cv(lambda) |> calc_UMGY_effect()  
```

::: {.noteblock data-latex=""}
In the above code snippet, the `calc_day_general_effect.cv` function is called internally from the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function, along with the [calc_UMGY_effect](#func.calc_UMGY_effect) function (both described below).
:::
:::

::: { #func.calc_day_general_effect.cv.args .sidebar }
##### Arguments
\

::: { #func.calc_day_general_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

::: { #func.calc_day_general_effect.cv.details .sidebar }
##### Details
\

Under the hood, this function internally calls the [calc_day_general_effect](#func.calc_day_general_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets]. It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.

::: {.noteblock data-latex=""}
The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_day_general_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

::: { #func.calc_day_general_effect.cv.value .sidebar }
##### Value
\

Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) *Date General Effect*.
:::

::: { #func.calc_day_general_effect.cv.code .sidebar }
##### Source Code
\

Below is a simplified version of the source code of the [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L33) function:
```{r eval=FALSE}
calc_day_general_effect.cv <- function(lambda = 0){

  date_general_effect_ls <- lapply(edx_CV,  function(cv_fold_dat){
    cv_fold_dat$train_set |> calc_day_general_effect(lambda)
  })
  put_log1("Function `calc_day_general_effect.cv`:
Date Global Effect list has been computed for %1-Fold Cross Validation samples.", 
           CVFolds_N)

  if(lambda == 0) put_log("Function `calc_day_general_effect.cv`:
Training completed: Date Global Effects model.")
  else put_log1("Function `calc_day_general_effect.cv`:
Training completed: Date Global Effects model for lambda: %1...",
                lambda)

::: {.noteblock data-latex=""}
The complete source code of the [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L33) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L33) script on _GitHub_.
:::
:::

#### [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) Function {#func.calc_UMGY_SmoothedDay_effect}
\

Builds the *User+Movie+Genre+Year Effect (UMGYDE) Model* based on the *Date General Effect* data structure returned by the [calc_date_general_effect](#func.calc_date_general_effect) or [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.

::: { #func.calc_UMGY_SmoothedDay_effect.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
  train_set |>
    calc_date_general_effect(lambda) |>
    calc_UMGY_SmoothedDay_effect()
```

::: {.noteblock data-latex=""}
In the code snippet above, the function `calc_UMGY_SmoothedDay_effect` is called internally from the [train_UMGY_effect](#func.train_UMGY_effect) function described below.
:::
:::

::: { #func.calc_UMGY_SmoothedDay_effect.args .sidebar }
##### Arguments
\

::: { #func.calc_UMGY_SmoothedDay_effect.args.date_general_effect .sidebar }
  - **date_general_effect:** Data frame representing the *Date General Effect*;

::: { #func.calc_UMGY_SmoothedDay_effect.details .sidebar }
##### Details
\

An example of using it in the [train_UMGY_effect](#func.train_UMGY_effect) function is shown above in the [Usage](#func.calc_UMGY_SmoothedDay_effect.usage) section of *This Description*:

::: { #func.calc_UMGY_SmoothedDay_effect.value .sidebar }
##### Value
\

Data frame representing the *UMGYDE Model*.
:::

::: { #func.calc_UMGY_SmoothedDay_effect.code .sidebar }
##### Source Code
\

The source code of the [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) function is shown below:
```{r eval=FALSE}
calc_UMGY_SmoothedDay_effect <- function(date_general_effect){
  date_general_effect |>
    group_by(year) |>
    summarise(ye = mean(de, na.rm = TRUE))
}
```

::: {.noteblock data-latex=""}
The source code of the [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) script on _GitHub_.
:::
:::

#### [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) Function {#func.train_UMGY_SmoothedDay_effect}
\

Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYDE) Model* using the training sample of the `Movielens` dataset passed in the [train_set](#func.train_UMGY_SmoothedDay_effect.args.train_set) argument.

::: { #func.train_UMGY_SmoothedDay_effect.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
  rglr.UMGYD_effect <- edx |> train_UMGY_SmoothedDay_effect(UMGYDE.rglr.best_lambda)
```
:::

::: { #func.train_UMGY_SmoothedDay_effect.args .sidebar }
##### Arguments
\

::: { #func.train_UMGY_SmoothedDay_effect.args.train_set .sidebar }
  - **train_set:** Training sample of the `Movielens` dataset;

:::
::: { #func.train_UMGY_SmoothedDay_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

::: { #func.train_UMGY_SmoothedDay_effect.details .sidebar }
##### Details
\

Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).

::: {.noteblock data-latex=""}
The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
:::
:::

::: { #func.train_UMGY_SmoothedDay_effect.value .sidebar }
##### Value
\

Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) *UMGY Effect Model*.
:::

::: { #func.train_UMGY_SmoothedDay_effect.code .sidebar }
##### Source Code
\

The source code of the [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is shown below:
```{r eval=FALSE}
train_UMGY_SmoothedDay_effect <- function(train_set, lambda = 0){
  if (is.na(lambda)) {
    stop("Function: train_UMGY_SmoothedDay_effect
`lambda` is `NA`")
  }

::: {.noteblock data-latex=""}
The source code of the [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) script on _GitHub_.
:::
:::

#### [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L113) Function {#func.train_UMGY_SmoothedDay_effect.cv}
\

Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYDE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

::: {.noteblock data-latex=""}
This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function (described below in section [UMGYDE Model: Regularization] of *This Appendix*) as shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) subsection of *This Function's Description Section* below.
:::

::: { #func.train_UMGY_SmoothedDay_effect.cv.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
  train_UMGY_SmoothedDay_effect.cv(lambda) |>
    calc_UMGY_effect_RMSE.cv()
```

::: {.noteblock data-latex=""}
In the above code snippet, the `train_UMGY_SmoothedDay_effect.cv` function is called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function, along with the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (both described below in [UMGYDE Model: Regularization] section and this section, respectively).
:::
:::

::: { #func.train_UMGY_SmoothedDay_effect.cv.args .sidebar }
##### Arguments
\

::: { #func.train_UMGY_SmoothedDay_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

::: { #func.train_UMGY_SmoothedDay_effect.cv.details .sidebar }
##### Details
\

Under the hood, this function internally calls the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).

::: {.noteblock data-latex=""}
The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
:::
:::

::: { #func.train_UMGY_SmoothedDay_effect.cv.value .sidebar }
##### Value
\

Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
:::

::: { #func.train_UMGY_SmoothedDay_effect.cv.code .sidebar }
##### Source Code
\

The source code of the [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L113) function is shown below:
```{r eval=FALSE}
train_UMGY_SmoothedDay_effect.cv <- function(lambda = 0){
  if (is.na(lambda)) {
    stop("Function: train_UMGY_SmoothedDay_effect.cv
`lambda` is `NA`")
  }

::: {.noteblock data-latex=""}
The source code of the [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L113) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L113) script on _GitHub_.
:::
:::

#### [UMGY_SmoothedDay_effect.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L125) Function {#func.UMGY_SmoothedDay_effect.predict}
\

Validates the *UMGY Effect (UMGYDE) Model* produced by the  [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call.

::: {.noteblock data-latex=""}
This helper function is used internally in the [UMGY_SmoothedDay_effect.predict.cv](#func.UMGY_SmoothedDay_effect.predict.cv) function (described below in this section) as shown in the [Usage](#func.UMGY_SmoothedDay_effect.predict.usage) subsection of *This Function's Description Section* below.
:::

::: { #func.UMGY_SmoothedDay_effect.predict.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
    cv_fold_dat$validation_set |> UMGY_SmoothedDay_effect.predict(UMGYD_effect)
```

::: {.noteblock data-latex=""}
In the code snippet above, the function `UMGY_SmoothedDay_effect.predict` is called internally from the [UMGY_SmoothedDay_effect.predict.cv](#func.UMGY_SmoothedDay_effect.predict.cv) function described below in this section.
:::
:::

::: { #func.UMGY_SmoothedDay_effect.predict.args .sidebar }
##### Arguments
\

::: { #func.UMGY_SmoothedDay_effect.predict.args.test_set .sidebar }
  - **test_set:** Validation dataset;

:::
::: { #func.UMGY_SmoothedDay_effect.predict.args.UMGYD_effect .sidebar }
  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.

::: { #func.UMGY_SmoothedDay_effect.predict.details .sidebar }
##### Details
\

The function calculates *Mean Squared Error (MSE)* for the *UMGYDE Model* passed in the [UMGYD_effect](#func.UMGY_SmoothedDay_effect.predict.args.UMGYD_effect) argument using the validation dataset passed in the [test_set](#func.UMGY_SmoothedDay_effect.predict.args.test_set) arg. 
:::

::: { #func.UMGY_SmoothedDay_effect.predict.value .sidebar }
##### Value
\

*MSE* value calculated for the *UMGYDE Model*.
:::

::: { #func.UMGY_SmoothedDay_effect.predict.code .sidebar }
##### Source Code
\

The source code of the [UMGY_SmoothedDay_effect.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L125) function is shown below:
```{r eval=FALSE}
UMGY_SmoothedDay_effect.predict <- function(test_set, UMGYD_effect){
  test_set |>
    left_join(edx.user_effect, by = "userId") |>
    left_join(rglr.UM_effect, by = "movieId") |>
    left_join(rglr.UMG_effect, by = "movieId") |>
    left_join(date_days_map, by = "timestamp") |>
    left_join(UMGYD_effect, by='year') |>
    mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
    pull(resid) |> mse()
}
```

::: {.noteblock data-latex=""}
The source code of the [UMGY_SmoothedDay_effect.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L125) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L125) script on _GitHub_.
:::
:::

#### [calc_UMGY_SmoothedDay_effect.MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L141) Function {#func.calc_UMGY_SmoothedDay_effect.MSE}
\

Validates the *UMGY Effect (UMGYDE) Model* produced by the  [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call.

::: {.noteblock data-latex=""}
This helper function is used internally in the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_SmoothedDay_effect.MSE.usage) subsection of *This Function's Description Section* below.
:::

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
    cv_fold_dat$validation_set |> calc_UMGY_SmoothedDay_effect.MSE(UMGYD_effect)
```

::: {.noteblock data-latex=""}
In the code snippet above, the function `calc_UMGY_SmoothedDay_effect.MSE` is called internally from the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) function described below in this section.
:::
:::

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args .sidebar }
##### Arguments
\

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set .sidebar }
  - **test_set:** Validation dataset;

:::
::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.UMGYD_effect .sidebar }
  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.details .sidebar }
##### Details
\

The function calculates *Mean Squared Error (MSE)* for the *UMGYDE Model* passed in the [UMGYD_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.args.UMGYD_effect) argument using the validation dataset passed in the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set) arg. 
:::

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.value .sidebar }
##### Value
\

*MSE* value calculated for the *UMGYDE Model*.
:::

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.code .sidebar }
##### Source Code
\

The source code of the [calc_UMGY_SmoothedDay_effect.MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L141) function is shown below:
```{r eval=FALSE}
calc_UMGY_SmoothedDay_effect.MSE <- function(test_set, UMGYD_effect){
  test_set |>
    left_join(edx.user_effect, by = "userId") |>
    left_join(rglr.UM_effect, by = "movieId") |>
    left_join(rglr.UMG_effect, by = "movieId") |>
    left_join(date_days_map, by = "timestamp") |>
    left_join(UMGYD_effect, by='year') |>
    mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
    pull(resid) |> mse()
}
```

::: {.noteblock data-latex=""}
The source code of the [calc_UMGY_SmoothedDay_effect.MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L141) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L141) script on _GitHub_.
:::
:::

#### [calc_UMGY_SmoothedDay_effect.MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L147) Function {#func.calc_UMGY_SmoothedDay_effect.MSE.cv}
\

Validates the *UMGY Effect (UMGYDE) Model* (produced by the [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

::: {.noteblock data-latex=""}
This helper function is used internally in the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.usage) subsection of *This Function's Description Section* below.
:::

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
  UMGY_effect_RMSE <- sqrt(calc_UMGY_SmoothedDay_effect.MSE.cv(UMGYD_effect))
```

::: {.noteblock data-latex=""}
In the code snippet above, the function `calc_UMGY_SmoothedDay_effect.MSE.cv` is called internally from the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described below in this section.
:::
:::

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args .sidebar }
##### Arguments
\

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.UMGYD_effect .sidebar }
  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.details .sidebar }
##### Details
\
